New lower bounds for Schur and weak Schur numbers

### 2021-09-23 article/article.tex

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
continuing on Rowley's "template"-based approach for Schur and Ramsey numbers. We also generalized the concept 
of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 
as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). The new lower 
bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
\(\WS (10) \geqslant 71\,256 \).

>>>>

This article provides new lower bounds for both Schur and weak Schur numbers. These results were obtained by 
exploiting a "template"-based approach for Schur and Ramsey numbers. This article also generalizes the concept 
of "template" to weak Schur numbers. Finding new templates allows us to get explicit partitions improving lower bounds 
as well as the growth rate for Schur numbers, weak Schur numbers and Ramsey numbers \(R_n(3)\). The new lower 
bounds include \(S(9) \geqslant 17\,803\), \(S(10) \geqslant 60\,948\), \(\WS(6) \geqslant 646\), \(\WS (9) \geqslant 22\,536\) and 
\(\WS (10) \geqslant 71\,256 \).
